---
name: Lorena Abad
position: "Researching the Environment through Geospatial Technologies"
address: |
         | Schillerstraße 30, 5020 Salzburg, Austria
profilepic: lore.jpg
phone: +43 662 8044 7582 
email: "lorena.abad@plus.ac.at"
twitter: loreabad6
github: loreabad6
linkedin: lorena-abad
researchgate: Lorena_Abad2
orcid: 0000-0003-0554-734X
headcolor: 009ACD
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    keep_tex: false
always_allow_html: yes
header-includes:
  \usepackage{float}
  \usepackage{multicol}
  \usepackage{colortbl}
  \arrayrulecolor{white}
  \usepackage{hhline}
  \definecolor{light-gray}{gray}{0.95}
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(ggplot2)
library(dplyr)
library(sf)
library(rnaturalearth)
library(sfnetworks)
library(ggrepel)
library(emojifont)
library(fontawesome)
library(kableExtra)
library(huxtable)
library(gridExtra)
```

```{r}
# \paragraphstyle{I am an environmental engineer from Cuenca, Ecuador specialized in Geospatial Technologies, expected by March 2019. My research scope includes spatial data analysis, particularly focused on R programming; remote sensing and earth observation data analysis, specially optical satellite imagery applied to environmental studies and analyses such as air pollution, land use/land cover change; geostatistical analysis of climate data; and ecological modelling. I feel very keen to pursue a career in research, science, and academia.}
```

<!-- | Nationality: Ecuadorian, Birthdate: 05/01/1994 -->

\faIcon{plane} My journey
============================

```{r edu_plot,fig.align='center', fig.width=6.5, fig.height=2.7, fig.showtext=TRUE}
load.fontawesome()
uni = fontawesome('fa-university')
work = fontawesome('fa-briefcase')
# teach = fontawesome('fa-chalkboard')

world = ne_countries("medium", returnclass = 'sf')
cities_geom = st_sfc(
    st_point(c(-79.00453,-2.90055)),
    st_point(c(-9.13333,38.71667)),
    st_point(c(7.6261,51.9607)),
    st_point(c(12.9864,47.8029))
  ) 

cities = st_sf(
  name = c('Cuenca, EC','Lisbon, PT','Münster, DE', 'Salzburg, AT'),
  geometry = cities_geom
  ) |>
  st_set_crs(4326) |>
  mutate(label = c(paste(work,uni, sep = " "), rep(uni,2), work))

routes = cities |> 
  as_sfnetwork() |> 
  st_as_sf('edges') |> 
   st_segmentize(units::set_units(100, m))

ggplot() +
  geom_sf(data = world, color = 'white', lwd = 0.1) +
  geom_sf_text(
    data = cities,
    aes(label = label),
    size = 3,
    color = '#009ACD',
    family = "fontawesome-webfont"
  ) +
  geom_sf(
    data = routes,
    color = '#009ACD',
    size = 0.5, alpha = 0.5,
    linetype = 'dotted'
  ) +
  coord_sf(
    crs = '+proj=robin',
    xlim = c(-10000000, 4500000),
    ylim = c(-650000,6500000)
  ) +
  theme_void() +
  theme(
    plot.margin = margin(-1, 0, -0.5, 0, "cm")
  )
```

\faIcon{briefcase} Professional Experience
============================================

```{r experience, eval = T}
exp = rorcid::orcid_employments("0000-0003-0554-734X") |>
  purrr::map(purrr::pluck, "affiliation-group", "summaries") |> 
  purrr::flatten_dfr()
names(exp) = stringr::str_remove(string = names(exp), pattern = "employment-summary.") 

exp |>
  filter(!stringr::str_detect(`role-title`, 'Teaching')) |>
  filter(!stringr::str_detect(`role-title`, 'Internship')) |> 
  mutate(`role-title` = case_when(
    stringr::str_detect(`department-name`, "Carrera de Ingeniería Ambiental") ~ "Research Assistant",
    TRUE ~ `role-title`
  )) |> 
  mutate(`start-date.month.value` = case_when(
    stringr::str_detect(`department-name`, "Carrera de Ingeniería Ambiental") ~ "03",
    TRUE ~ `start-date.month.value`
  )) |> 
  mutate(`end-date.year.value` = case_when(
   stringr::str_detect(`department-name`, "Carrera de Ingeniería Ambiental") ~ "2017",
    TRUE ~ `end-date.year.value`
  )) |>
  mutate(`end-date.month.value` = case_when(
    stringr::str_detect(`department-name`, "Carrera de Ingeniería Ambiental") ~ "08",
    TRUE ~ `end-date.month.value`
  )) |> 
  mutate(count = c(7,1,1,1,1)) |> 
  tidyr::uncount(count) |> 
  mutate(description = c(
    'Remote sensing and GIS specialist studying natural geohazards in the Risk, Hazard & Climate research group for different projects:',
    'SliDEM: Assessing the suitability of DEMs derived from Sentinel-1 for landslide volume estimation | Role: Python package developer.',
    'MontEO: The impact of mass movements on alpine trails and huts assessed by EO data | Role: Susceptibility mapping.',
    'STEC: Smarter Targeting of Erosion Control | Role: Mapping geomorphological features with deep learning and knowledge-based techniques.',
    'RiCoLa: Detection and Analysis of Landslide-induced River Course Changes and Lake Formation.',
    'MORPH: Mapping, Monitoring and Modelling the Spatio-Temporal Dynamics of Land Surface Morphology.',
    'citizenMorph: Observation and Reporting of Landscape Dynamics by Citizens.',
    'Spatio-temporal data analyst for the project: "Study of Cyclists and Pedestrian Mobility Patterns in Cuenca for a Sustainable Mobility".',
    'CEDIA project "Geo-statistical Inference of Meteorological Data for Azuay and Chimborazo provinces".',
    'Project "Water Quality and Environmental Variables Monitoring in Artificial Habitats for Endangered Species in Cuenca".',
    'Project "Determination of Particulate Matter PM10, PM2.5, and noise in Cuenca canton".'
    #\\href{http://monteo.zgis.at/}{\\textit{MontEO}}
    # 'Remote Sensing course for the Environmental Engineering Career from the University of Cuenca.',
    # 'Introduction to Physics course for the Environmental Engineering Career from the University of Cuenca.'
    # "Cartographic data gathering organization, topographic correction and categorization of urban land uses, scientific papers analysis for bibliographic review.",
    # "Assess the functioning state of Davis Station sensors, identify similarities and differences of two river basins hydrograms, analyze the effects of temperature and relative humidity on reference evapotranspiration calculation."
  )) |>
  detailed_entries(
    with = paste(`role-title`, `department-name`, sep = ' - '),
    when = paste(
      paste(`start-date.month.value`,`start-date.year.value`, sep = ', '),
      ifelse(is.na(`end-date.year.value`),"Present",paste(`end-date.month.value`,`end-date.year.value`, sep = ', ')),
      sep = ' - '
    ),
    what = organization.name,
    where = paste(organization.address.city,organization.address.country, sep =', '),
    why = description,
    .protect = TRUE
  )
```

<!--
\faIcon{chalkboard} Teaching Experience
============================================

```{r teaching, eval = T}
exp |>
  filter(stringr::str_detect(`role-title`, 'Teaching')) |> 
  mutate(description = c(
    'Remote Sensing course for the Environmental Engineering Career from the University of Cuenca.',
    'Introduction to Physics course for the Environmental Engineering Career from the University of Cuenca.'
  )) |>
  detailed_entries(
    with = paste(`role-title`, `department-name`, sep = ' - '),
    when = paste(
      paste(`start-date.month.value`,`start-date.year.value`, sep = ', '),
      ifelse(is.na(`end-date.year.value`),"Present",paste(`end-date.month.value`,`end-date.year.value`, sep = ', ')),
      sep = ' - '
    ),
    what = organization.name,
    where = paste(organization.address.city,organization.address.country, sep =', '),
    why = description
    # .protect = FALSE
  )
```
-->
\faIcon{university} Education
==================================

```{r education}
tribble(
  ~ study, ~ university, ~ loc, ~ dates, ~ details,
    "Erasmus Mundus Msc. Geospatial Technologies", "Universidade Nova de Lisboa \\& Westfälische Wilhelms-Universität Münster ","Lisbon, PT \\& Münster, DE", "2017 - 2019", "Geospatial Data Mining, Geostatistics, Remote Sensing, Geographic Information Science, Spatial Data Science with R and Python, Unmanned Aerial Systems.",
    "Erasmus Mundus Msc. Geospatial Technologies", "Universidade Nova de Lisboa \\& Westfälische Wilhelms-Universität Münster ","Lisbon, PT \\& Münster, DE", "2017 - 2019", "Masters Thesis: Validating a bike network analysis score based on open data as a connectivity measure of urban cycling infrastructure adapted for European cities. Supervised by Prof. Dr. Edzer Pebesma. URL: \\textit{http://hdl.handle.net/10362/67511}",
  "Environmental Engineer BSc.", "Universidad de Cuenca", "Cuenca, EC", "2011 - 2016", "Environmental Studies, Natural Resources Management, Cartography, Remote Sensing, Ecology, Hydrology, Meteorology and Climatology, among 66 subjects.",
  "Environmental Engineer BSc.", "Universidad de Cuenca", "Cuenca, EC", "2011 - 2016", "Bachelor Thesis (in spanish): Particulate Matter less than 10 microns concentration estimation through Remote Sensing in the Urban Area of Cuenca city. Supervised by MSc. Danilo Mejía Coronel. URL: \\textit{http://dspace.ucuenca.edu.ec/handle/123456789/25484}",
) |> 
  detailed_entries(study, dates, university, loc, details, .protect=FALSE)
```

\faIcon*{file} Selected Publications
===========================

\footnotesize

For a complete list of publications see [*my Google Scholar profile*](https://scholar.google.com/citations?user=vDqPwpUAAAAJ&hl=en).

- Dabiri, Z., Hölbling, D., **Abad, L.**, Guðmundsson, S. (2021). [*Comparing the Applicability of Sentinel-1 and Sentinel-2 for Mapping the Evolution of Ice-marginal Lakes in Southeast Iceland*](https://doi.org/10.1553/giscience2021_01_s46). GI_Forum, 1(1), 46–52.
<!-- - Dabiri, Z., Hölbling, D., **Abad, L.**, Helgason, J. K., Sæmundsson, Þ., Tiede, D. (2020). [*Generation of Multi-Temporal Dems from Sentinel-1 for Assessing Geomorphological Changes in the Hítardalur Valley, Western Iceland*](https://doi.org/10.1130/abs/2020AM-357105). Geological Society of America Abstracts with Programs, 52 (6). -->

- Dabiri, Z., Hölbling, D., **Abad, L.**, Helgason, J. K., Sæmundsson, Þ., Tiede, D. (2020). [*Assessment of Landslide-Induced Geomorphological Changes in Hítardalur Valley, Iceland, Using Sentinel-1 and Sentinel-2 Data*](https://doi.org/10.3390/app10175848). Applied Sciences, 10(17), 5848.

- Hennig, S., **Abad, L.**, Hölbling, D., Tiede, D. (2020). [*Implementing Geo Citizen Science Solutions: Experiences from the citizenMorph Project*](https://doi.org/10.1553/giscience2020). Journal for Geographic Information Science, 7(2), 3–14.

- **Abad, L.**, Hölbling, D., Spiekermann, R., Dabiri, Z., Prasicek, G., Argentin, A.-L. (2020). [*Mapping and monitoring of landslide-dammed lakes using Sentinel-2 time series -a case study after the 2016 Kaikōura Earthquake in New Zealand*](https://doi.org/10.5194/egusphere-egu2020-572). EGU General Assembly 2020.

- Hölbling, D., **Abad, L.**, Dabiri, Z., Prasicek, G., Tsai, T.-T., Argentin, A.-L. [*Mapping and Analyzing the Evolution of the Butangbunasi Landslide Using Landsat Time Series with Respect to Heavy Rainfall Events during Typhoons*](https://doi.org/10.3390/app10020630). Applied Sciences. 2020, 10, 630.

- **Abad, L**., van der Meer, L. (2018). [*Quantifying Bicycle Network Connectivity in Lisbon Using Open Data*](https://doi.org/10.3390/info9110287). Information, 9(11), 14.

\normalsize

<!--
\faIcon{lightbulb} Projects
=====================================

\smallskip

\faIcon{satellite} Research projects
---------------------------------
<!-- \par\noindent\nobreak\vspace{-30pt}\rule{\textwidth}{1pt} -->

<!--
```{r proj}
tribble(
  ~ name, ~ acronym, ~ date, ~study_area,
  "Smarter Targeting of Erosion Control", "STEC", "2018 - 2023", "NZ", 
  "The impact of mass movements on alpine trails and huts assessed by EO data", "MontEO \\href{http://monteo.zgis.at/}{\\tiny{\\faIcon{link}}}", "2020 - 2021", "AT", 
  "Detection and Analysis of Landslide-induced River Course Changes and Lake Formation", "RiCoLa \\href{http://landslides-and-rivers.sbg.ac.at/}{\\tiny{\\faIcon{link}}}", "2017 - 2020", "AT, NZ, TW", 
  "Observation and Reporting of Landscape Dynamics by Citizens", "citizenMorph \\href{http://citizenmorph.sbg.ac.at/}{\\tiny{\\faIcon{link}}}", "2018 - 2020", "AT, DE, IS", 
  "Mapping, Monitoring and Modelling the Spatio-Temporal Dynamics of Land Surface Morphology", "MORPH \\href{http://morph.sbg.ac.at/}{\\tiny{\\faIcon{link}}}", "2016 - 2020", "IS"
) |> 
  detailed_entries(with = acronym, what = name, when = date, where = study_area, .protect=FALSE)  
```

\smallskip

\faIcon{laptop-code} Programming projects
----------------------------------
<!-- \par\noindent\nobreak\vspace{-30pt}\rule{\textwidth}{1pt} -->

<!--
```{r dev}
tribble(
  ~ name, ~ acronym, ~ type,
  "Landslide dammed-lakes detection and monitoring after the Kaikoura earthquake in New Zealand", "Kaikoura landslide dammed-lakes \\href{https://github.com/loreabad6/KaikouraDammedLakes_public}{\\tiny{\\faIcon{link}}}", "GEE project",
  "Tidy Geospatial Networks in R", "sfnetworks \\href{https://luukvdmeer.github.io/sfnetworks/}{\\tiny{\\faIcon{link}}}", "R Package",
  "Bicycle Network Analysis Score for UK and NL",
  "BNA-EU \\href{https://github.com/loreabad6/masters-thesis-geotech}{\\tiny{\\faIcon{link}}}", "RMarkdown Reporting"
) |> 
  detailed_entries(with = acronym, what = name, where = type, .protect=FALSE)  
```
-->
<!--

\faIcon{comments} Presentations, blogs, courses
================================

```{r presentations}
tribble(
  ~ title, ~ link, ~ event, ~ date,
  "Mapping and monitoring landslide-dammed lakes in Kaikōura, New Zealand, using the Google Earth Engine", "Lightning Talk at the Geo For Good 2020 Summit Public Sector Meetup \\href{https://www.youtube.com/watch?v=CbHYkUpCwCI&ab_channel=GoogleEarth}{\\tiny{\\faIcon{link}}}", "Geo for Good 2020", "10, 2020",
  "El rol de las tecnologías geoespaciales para el mapeo y monitoreo de peligros naturales", "Invited talk at the event 'Voces de la Ingeniería Ambiental' \\href{https://loreabad6.github.io/VocesAmbiental/presentacion.html}{\\tiny{\\faIcon{link}}}", "Voces Ambiental 2020", "09, 2020",
  "Bicycle Network Analysis for assessing cyclability", "Presentation during Cycling Potential Hackathon: Lisbon \\href{https://github.com/U-Shift/cyclingpotential-hack}{\\tiny{\\faIcon{link}}}", "U-Shift event", "09, 2020",
  "Implementing geo citizen science solutions: experiences from the citizenMorph project", "Full paper presentation in session C43: Spatial Citizens Science \\href{https://www.conftool.com/giweek2020/index.php?page=browseSessions&form_session=202}{\\tiny{\\faIcon{link}}}", "Gi-Forum 2020", "07, 2020",
  "Tidy Geospatial Networks in R: Introducing the sfnetworks package", "Webinar \\& Hackathon \\href{https://sfnetworks.github.io/sfnetworks-webinar/slides}{\\tiny{\\faIcon{link}}}", "e-Rum 2020 satellite event", "06, 2020",
  "Mapping and monitoring of landslide-dammed lakes using Sentinel-2 time series", "Display in session Natural Hazards NH6.1 \\href{https://presentations.copernicus.org/EGU2020/EGU2020-572_presentation.pdf}{\\tiny{\\faIcon{link}}}", "EGU 2020", "05, 2020",
  "Intro to spatial vector data analysis with R","R spatial crash course \\href{https://luukvdmeer.github.io/maptimeR/exercises.html}{\\tiny{\\faIcon{link}}}", "Maptime Salzburg", "02, 2020",
  "Spatial networks in R with sf and tidygraph", "Blogpost \\href{https://www.r-spatial.org/r/2019/09/26/spatial-networks.html}{\\tiny{\\faIcon{link}}}", "r-spatial blog", "09, 2019",
  "Bicycle Network Analysis for Lisbon", "Short Paper Presentation in the 2nd Open Data for Open Cities Workshop \\href{https://github.com/GeoTecINIT/OpenData4OpenCities/blob/master/Presentations/AGILE_2018_Presentation_Abad-vdMeer.pdf}{\\tiny{\\faIcon{link}}}", "AGILE Workshop: OD4OC", "06, 2018",
  "Exploring Space-Time Patterns Of Volunteered Cycling Data In An Intermediate City", "Abstract Presentation", "GeoMundus 2017", "11, 2017"
) |> 
  detailed_entries(with = title, what = link, where = event, when = date, .protect=FALSE)  
```
-->

\faIcon{medal} Awards & Distinctions
===============================

```{r dist}
tribble(
  ~ area, ~ org, ~ date,
  "ISC funding for {sfnetworks}", "R-Consortium", "2019",
  "Benigno Malo Prize - University Honors Award", "Universidad de Cuenca", "2018",
  "AGILE 2018 conference - travel grant", "AGILE \\& ESRI", "2018",
  "Erasmus Mundus Scholarship", "European Commission", "2017",
  # "Best Scientific Poster - 2nd International Summer School \\newline 
# ``The Biodiversity of Genes, Species and Ecosystems''", "Universität Osnabrück","2015",
  "Vanguardia Honors Program", "Universidad de Cuenca", "2014 - 2016"
) |> 
  brief_entries(what = area, when = date, with = org, .protect = F)
```

\faIcon{hand-holding-heart} Volunteer work
===============================

```{r vol}
tribble(
  ~ desc, ~ date,
  "Group Peer Mentor in Women in Geospatial+ Mentorship Program", "2020-2021"
) |> 
  brief_entries(what = desc, when = date, .protect = F)
```

<!-- 
\faIcon{users} Memberships
===============================
```{r org}
tribble(
  ~ org, ~ date,
  "R-Ladies Global \\href{https://rladies.org/austria-rladies/name/lorena-abad/}{\\tiny{\\faIcon{link}}}", "since 2020",
  "Women in Geospatial \\href{https://speakers.womeningeospatial.org/speakers}{\\tiny{\\faIcon{link}}}", "since 2020",
  "European Geosciences Union", "since 2020",
  "Erasmus Mundus Association", "since 2020"
) |> 
  brief_entries(what = org, when = date, .protect = F)
```
-->

\faIcon{brain} Skills
================================

\smallskip

\faIcon{cogs} Technical skills
---------------------------------
<!-- \noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}} -->

<!-- \par\noindent\nobreak\vspace{-30pt}\rule{\textwidth}{1pt} -->

```{r techtable, results='markup'}
tribble(
   ~`Coding Languages`, ~Software, ~Other,
  "R -- Python -- SQL -- JavaScript",
  "QGIS -- Earth Engine -- RStudio -- SAGA -- PostgreSQL -- ArcGIS -- eCognition -- GIMP -- Mendeley",
  "Git -- Markdown -- LaTex -- OpenStreetMap"
) |>
  kable(booktabs = T, align = 'c', escape = F, format = "latex") |>
  kable_styling(full_width = F, font_size = 9, latex_options = "HOLD_position") |> 
  row_spec(0, bold = T, color = "#009acd") |> 
  row_spec(1, bold = F, color = "#7f7f7f") |> 
  column_spec(column = 1:3, width = '4.75cm')
```

<!-- \smallskip -->

<!--
\faIcon{calendar} Organizational skills
------------------------------
```{r events}
tribble(
  ~ event, ~ date, ~ place,
  "e-Rum 2020 satellite event: \\textit{sfnetworks} Webinar and Hackathon \\href{https://2020.erum.io/program/hackathon/}{\\tiny{\\faIcon{link}}}", "06, 2020", "Online Event",
  "citizenMorph App Testing Workshop", "09, 2019", "Höfn, IS",
  "GeoMundus 2018 \\href{http://www.geomundus.org/2018/}{\\tiny{\\faIcon{link}}}", "12, 2018", "Lisbon, PT",
  # "I University Simposium of Environmental Science Research", "06, 2016", "Cuenca, EC",
  "Vicepresident of the Student Association of Environmental Engineers", "2013 - 2014", "Cuenca, EC",
) |> 
  brief_entries(what = event, when = date, with = place, .protect = F)
```
  -->
  
\bigskip

\faIcon{language} Languages
-------------------------------

```{r langforeign, results='markup'}
data.frame(
  Skill = c("Reading", "Writing", "Listening","Speaking"),
  Spanish = cell_spec(c(rep("Native", 4)), 'latex', color = '#005c7b'), 
  English = cell_spec(c("C2","C1","C2","C2"), 'latex', color = '#009acd'), 
  French = cell_spec(c("B2","B2","B2","B2"), 'latex', color = '#4cb8dc'), 
  German = cell_spec(c("B1","B1","B1","B1"), 'latex', color = '#4cb8dc'), 
  Portuguese = cell_spec(c("B1","B1","B1","B1"), 'latex', color = '#4cb8dc'), 
  Dutch = cell_spec(c("A2","A1","A2","A2"), 'latex', color = '#7fcce6') 
) |>
  kable(booktabs = T, align = 'c', escape = F, format = "latex") |>
  kable_styling(full_width = F, font_size = 9, latex_options = "HOLD_position") |> 
  footnote(
    footnote_as_chunk = T,
    general_title = " ",
    general = "\\\\tiny Common European Framework of Reference for Languages: A1/A2: Basic User. B1/B2: Independent User. C1/C2: Proficient User",
    escape = F
  ) |>
  column_spec(column = 1:6, width = '2.4cm') #|> 
  # add_header_above(' ', line = F) |>
  # row_spec(0:4, extra_latex_after = "\\arrayrulecolor{white}") 
```

\faIcon{comment} References
=============================

\footnotesize

- **Prof. Dr. Edzer Pebesma**, Institute for Geoinformatics, WWU, edzer.pebesma@uni-muenster.de

- **Prof. Dr. Marco Painho** NOVA Information Management School, painho@novaims.unl.pt

- **Dr. Daniel Hölbling**, Department of Geoinformatics - Z\_GIS, PLUS, daniel.hoelbling@plus.ac.at

\normalsize

<!-- \footnotesize -->
<!-- \begin{multicols}{3} -->
<!-- \begin{center} -->

<!-- \textbf{Prof. Dr. Edzer Pebesma} \newline -->
<!-- \faIcon{phone} +49 251 83-33081 \newline -->
<!-- \faIcon{at} edzer.pebesma@uni-muenster.de \newline -->
<!-- \faIcon{envelope} Institute for Geoinformatics \newline -->
<!-- Heisenbergstraße 2, \newline -->
<!-- 48149 Münster, Germany -->

<!-- \textbf{Prof. Dr. Marco Painho} \newline -->
<!-- \faIcon{phone} +351 213 871 573 \newline -->
<!-- \faIcon{at} painho@novaims.unl.pt \newline -->
<!-- \faIcon{envelope} NOVA Information Management School \newline -->
<!-- Campus de Campolide\newline -->
<!-- 1070-312 Lisbon, Portugal -->

<!-- \textbf{Mag. Daniel Hölbling} \newline -->
<!-- \faIcon{phone} +43 (0)662 8044 7581 \newline -->
<!-- \faIcon{at} daniel.hoelbling@plus.ac.at \newline -->
<!-- \faIcon{envelope} Department of Geoinformatics - Z\_GIS 'newline -->
<!-- Schillerstrasse 30 \newline -->
<!-- 5020 Salzburg, Austria -->
<!-- \end{center} -->
<!-- \end{multicols} -->

<!-- \normalsize -->
